### 2019-04-24 README.Rmd
Updated README to include line on metaverse
Add hex sticker, thanks to Eliza Grames

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  fig.width= 12, 
  fig.height=3)
```
# `robvis`: an R pacakge for quick visualisation of risk-of-bias assessment results

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  fig.width= 12, 
  fig.height=3)
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

Part of the [metaverse](https://github.com/rmetaverse/metaverse)
